\Title

### 2021-06-28 manuscript/content.tex
Define M_k and fix summation equation
The position vector is not q_j but q_k_j.

\begin{enumerate}
  \item Define a set of $M$ equivalent sources distributed throughout the
    survey area (see section \ref{sec:source_distribution} for details).
  \item Define a set of $K$ overlapping windows of equal size that cover the
    survey area.
  \item Create $K$ separate sets of equivalent sources, one for each window.
    Each set will be formed by the portion of the original $M$ sources that
    fall inside the respective window.
    Since the windows overlap, the total number of sources from all sets will
    be greater than $M$.
  \item Define vector $\mathbf{c}_k$ as the coefficients of the equivalent
    sources of the $k$-th window.
  \item Define matrix $\mathbf{A}_k$ as the Jacobian matrix between the sources
    in the $k$-th window and all $N$ data points of the survey.
  \item Model the predicted data as a superposition of the effects of the $K$
    separate sets of equivalent sources (i.e., Eq.~\ref{eq:gb-linear-model}).
\end{enumerate}

The gradient boosting algorithm works by fitting each component of the
additive model, one at a time, to the residuals of the previous component.
\citet{friedman2001} demonstrates that this corresponds to a steepest-descent
optimization in the so-called ``function space''.
The adaptation of the gradient boosting method to find the damped least-squares
solutions for the $K$ parameters vectors $\mathbf{c}_k$ in
Eq.~\ref{eq:gb-linear-model} is presented in
Algorithm~\ref{alg:gradient_boosting}.

    calculate $N \times M_k$ Jacobian matrix $\mathbf{A}_k$
    \;

@@

\begin{equation}
    d(\mathbf{p}) =
    \sum\limits_{k=1}^K \sum\limits_{j=1}^{M_k}
    \frac{{c_k}_j}{\left\lVert \mathbf{p} - \mathbf{q}_j \right\rVert}
    \ ,
\end{equation}

\noindent where ${c_k}_j$ is the $j$-th element of the $\mathbf{c}_k$ vector.

>>>>

\begin{enumerate}
  \item Define a set of $M$ equivalent sources distributed throughout the
    survey area (see section \ref{sec:source_distribution} for details).
  \item Define a set of $K$ overlapping windows of equal size that cover the
    survey area.
  \item Create $K$ separate sets of equivalent sources, one for each window.
    Each set will be formed by the portion of the original $M$ sources that
    fall inside the respective window.
    Since the windows overlap, the total number of sources from all sets will
    be greater than $M$.
  \item Define vector $\mathbf{c}_k$ as the $M_k$ coefficients of the
    equivalent sources of the $k$-th window.
  \item Define matrix $\mathbf{A}_k$ as the $N \times M_k$ Jacobian matrix
    between the sources in the $k$-th window and all $N$ data points of the
    survey.
  \item Model the predicted data as a superposition of the effects of the $K$
    separate sets of equivalent sources (i.e., Eq.~\ref{eq:gb-linear-model}).
\end{enumerate}

The gradient boosting algorithm works by fitting each component of the
additive model, one at a time, to the residuals of the previous component.
\citet{friedman2001} demonstrates that this corresponds to a steepest-descent
optimization in the so-called ``function space''.
The adaptation of the gradient boosting method to find the damped least-squares
solutions for the $K$ parameter vectors $\mathbf{c}_k$ in
Eq.~\ref{eq:gb-linear-model} is presented in
Algorithm~\ref{alg:gradient_boosting}.

\begin{algorithm}[!h]
  \DontPrintSemicolon
  \setstretch{1.5}
  Define the residual vector $\mathbf{r}_{0} = \mathbf{d}^o$ \;
  \For{ $k = 1$ \KwTo $K$ }{

    Calculate the $N \times M_k$ Jacobian matrix $\mathbf{A}_k$
    \;

@@

\begin{equation}
    d(\mathbf{p}) =
    \sum\limits_{k=1}^K \sum\limits_{j=1}^{M_k}
    \frac{{c_k}_j}{\left\lVert \mathbf{p} - {\mathbf{q}_k}_j \right\rVert}
    \ ,
\end{equation}

\noindent
in which ${c_k}_j$ is the $j$-th element of the $\mathbf{c}_k$ vector and the
${\mathbf{q}_k}_j$ is the position vector of the $j$-th source of the $k$-th
window.
